Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-22 robdml.tex
update

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to the security implications of adversarial vulnerability, the
	adversarial robustness of deep metric learning models have to be improved
	via defense.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing methods refrain from using the min-max adversarial
	training, but instead learns from a weak adversary inefficiently.
	% our starting point
	Conversely, we argue that a model can learn from a strong adversary without
	collapse, where the key is triplet hardness.
	% HM framework
	To this end, Hardness Manipulation is proposed to adversarially perturb the
	training triplet to increase its hardness into a specified level, by
	referencing another benign triplet or a pseudo-hardness function.
	% GA Adversary
	Based on this, Gradual Adversary is proposed as a family of pseudo-hardness
	functions to overcome problems of referencing other benign triplets, and
	achieve a better balance in the learning objective.
	% Intra-Class Structure
	Besides, a penalty on Intra-Class Structure among benign and adversarial
	examples can further improve model robustness, which is neglected by
	previous methods.
	% Experiment and Conclusion
	Comprehensive experimental results on three commonly used deep metric
	learning datasets suggest that the proposed method overwhelmingly
	outperforms the state-of-the-art defense methods in terms of robustness,
	training cost, as well as recall performance on benign examples, while
	remains in a simple form.
%
\end{abstract}

@@

Despite the advancements in this field thanks to deep neural
networks, recent studies find DML models vulnerable to
adversarial attacks, where an imperceptible perturbation can incur unexpected
retrieval, or covertly manipulate the results~\cite{advrank,advorder}.
%
Such vulnerability raises security, safety, and fairness concerns in the
DML applications.
%
For example, impersonation or recognition evation are possible for a
vulnerable DML-based face-identification system.
%
To counter the attacks (\ie, mitigating the vulnerability), the
\emph{adversarial robustness} of DML models has to be improved via defense.

@@

% existing methods & problem
Existing defense methods for DML~\cite{advrank,robrank} are adversarial
training-based, inspired by Madry's \emph{min-max} adversarial
training~\cite{madry} because it is one of the most effective methods for deep
neural network classifiers.
%
Specifically, Madry's method involves a inner problem to \emph{maximize} the
loss by perturbing the inputs into adversarial examples, and an outer problem
to \emph{minimize} the loss by updating the model parameters.
%
However, in order to avoid model collapse, the existing DML defenses refrain
from directly adopting such paradigm, but instead use some indirect and
relatively weak objectives to merely increase the loss value to a certain
level.
%
As a result, the model is not learning from a strong adversary, and suffers
from low efficiency in gaining robustness within limited time. 
%
Furthermore, advertsarial training already suffers from
significant training time cost (compared to the normal training process).
%
Hence, time efficiency in gaining adversarial robustness is an inevitable
major issue.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to the security implications of adversarial vulnerability, the
	adversarial robustness of deep metric learning models have to be improved
	via defense.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing methods refrain from using the min-max adversarial training, but
	instead learns from a weak adversary inefficiently.
	% our starting point
	Conversely, we argue that a model can learn from a strong adversary without
	collapse, where the key is triplet hardness.
	% HM framework
	To this end, Hardness Manipulation is proposed to adversarially perturb the
	training triplet to increase its hardness into a specified level, by
	referencing another benign triplet or a pseudo-hardness function.
	% GA Adversary
	Based on this, Gradual Adversary is proposed as a family of pseudo-hardness
	functions to overcome problems of referencing other benign triplets, and
	achieve a better balance in the learning objective.
	% Intra-Class Structure
	Besides, a penalty on Intra-Class Structure among benign and adversarial
	examples can further improve model robustness, which is neglected by
	previous methods.
	% Experiment and Conclusion
	Comprehensive experimental results on commonly used deep metric
	learning datasets suggest that the proposed method, although simple in
	form, overwhelmingly outperforms the state-of-the-art defense methods in
	terms of training time cost, robustness, as well as recall performance on
	benign examples.
%
\end{abstract}

@@

Despite the advancements in this field thanks to deep neural
networks, recent studies find DML models vulnerable to
adversarial attacks, where an imperceptible perturbation can incur unexpected
retrieval, or covertly manipulate the results~\cite{advrank,advorder}.
%
Such vulnerability raises security, safety, and fairness concerns in the
DML applications.
%
For example, impersonation or recognition evasion are possible for a
vulnerable DML-based face-identification system.
%
To counter the attacks (\ie, mitigating the vulnerability), the
\emph{adversarial robustness} of DML models has to be improved via defense.

@@

% existing methods & problem
Existing defense methods for DML~\cite{advrank,robrank} are adversarial
training-based, inspired by Madry's \emph{min-max} adversarial
training~\cite{madry} because it is one of the most effective methods for deep
neural network classifiers.
%
Specifically, Madry's method involves a inner problem to \emph{maximize} the
loss by perturbing the inputs into adversarial examples, and an outer problem
to \emph{minimize} the loss by updating the model parameters.
%
However, in order to avoid model collapse, the existing DML defenses refrain
from directly adopting such paradigm, but instead use some indirect and
relatively weak objectives to merely increase the loss value to a certain
level.
%
As a result, the model is not learning from a strong adversary, and suffers
from low efficiency in gaining robustness within limited time. 
%
Furthermore, adversarial training already suffers from significant training
time cost (compared to the normal training process).
%
Hence, time efficiency in gaining adversarial robustness
is an inevitable major issue.

% we argue

As suggested by previous works, an appropriate adversary for the inner
\emph{maximization} problem should increase the loss to a certain point between
that of benign examples (\ie, unperturbed examples) and the theoretical upper
bound.
%
What if this point is reached by the strongest adversary, directly and
efficiently?
%
Besides, as the mathematical expectation of loss is also greatly influenced by
the triplet sampling strategy, we conjecture that the triplet sampling strategy
and triplet ``hardness'' have a key impact for adversarial training.
